---
title: "BT Extensions Week 1"
output: html_notebook
---

23/7/2018:

Repurposing "BayesBT" (Matlab) for R
 - Note most of the below stuff has already been tested but is the completed functionally code for the new testing which will be Titled "Active Testing : -------"

Test input parameters

```{r}
library("Matrix")

wh = Matrix(c(0,1,4,2,0,5,1,1,0), ncol = 3, nrow = 3)
lh = Matrix(c(0,3,1,3,0,0,1,0,0), nrow= 3, ncol = 3)
theta = 1.5
iteration = 1
a = 5
prec = 1e-8
a_th = 2
b_th = 1

```

Parameter Initializaton

```{r}

K = length(wh[,1]) # Number of teams or players
b = K*a - 1 # 
lambda = array(1, K) # Skill vector
iter_max = 5000 # Max iterations

pi_st = Matrix(array(0, iter_max*K), nrow = iter_max, ncol = K) # Values of the normalized skills at each iteration
theta_st = Matrix(array(0, iter_max), nrow = iter_max, ncol = 1) # Values of home ground advantage at each iteration
ell = Matrix(array(0, iter_max),nrow = iter_max, ncol = 1) # Log posterior at each iteration

N = wh + lh # number of games between i and j where i is at home
ak = a - 1 + sum(wh + lh, 2)
H = sum(sum(wh)) # total number of home field wins
change = .Machine$double.xmax # Machine maximum

dims = which(N != 0, arr.ind = TRUE) # dimensions of N which are indices
ind_i = dims[,1] # i values of the sparse matrix
ind_j = dims[,2] # j values of the sparse matrix
N_sparse = N[dims] # Sparse N matrix

theta = 1.5 # arbitrary theta
iteration = 1
```

Active Testing: Log Posterior calculations

Initialize a sparse matrix containing our initial log-posteriors
```{r}

Z2 = sparseMatrix(ind_i, ind_j, x = Matrix(N_sparse*log(theta*lambda[ind_i] + lambda[ind_j]))) 

```

Update 'ell' our iterative log-posterior

```{r}

ell[iteration] = (a_th - 1 + H)*log(theta) - b_th * theta + log(lambda) * (a-1 + sum(wh + lh, 2)) - b * sum(lambda) - sum(sum(Z2))

```




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

